Analysis of Bauer et al. (2023) bioRxiv: <br> Favourable Conservation Status (FCS)

### 2023-03-01 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

---
title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)"
author: "<b>Markus Bauer</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: png
    fig_width: 7
    fig_height: 5
editor_options: 
  markdown: 
    wrap: 72
---

@@

#### Prior predictive check - Kernel density (BARG 1.E)

```{r prior-predictive-check}
bayesplot::ppc_dens_overlay(y, yrep_prior[1:500, ])
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$site) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$exposition) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$survey_year_fct) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$target_type) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$seed_density) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$sand_ratio) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$substrate_depth) +
  coord_cartesian(xlim = c(-2, 2))
```

@@

```{r effect-sizes}
posterior1 %>%
  posterior::summarize_draws() %>%
  knitr::kable()
emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
          survey_year_fct, type = "response")
emm$emmeans
```

```{r write-csv, echo = FALSE}
write.csv(draws1, here("outputs", "statistics", "table_fcs.csv"))
```

>>>>

---
title: "Analysis of Bauer et al. (2023) bioRxiv: <br> Favourable Conservation Status (FCS)"
author: "<b>Markus Bauer</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: png
    fig_width: 7
    fig_height: 5
editor_options: 
  markdown: 
    wrap: 72
---

@@

#### Prior predictive check (BARG 1.E)

```{r prior-predictive-check}
bayesplot::ppc_stat(y, yrep_prior[1:500, ], binwidth = 0.5) +
  coord_cartesian(xlim = c(-4, 4))
ppc_stat_grouped(
  y, yrep_prior[1:500, ], group = sites$site, binwidth = 0.5
  ) +
  coord_cartesian(xlim = c(-4, 4))
ppc_stat_grouped(
  y, yrep_prior[1:500, ], group = sites$exposition, binwidth = 0.5
  ) +
  coord_cartesian(xlim = c(-4, 4))
ppc_stat_grouped(
  y, yrep_prior[1:500, ], group = sites$survey_year_fct, binwidth = 0.5
  ) +
  coord_cartesian(xlim = c(-4, 4))
ppc_stat_grouped(
  y, yrep_prior[1:500, ], group = sites$target_type, binwidth = 0.5
  ) +
  coord_cartesian(xlim = c(-4, 4))
ppc_stat_grouped(
  y, yrep_prior[1:500, ], group = sites$seed_density, binwidth = 0.5
  ) +
  coord_cartesian(xlim = c(-4, 4))
ppc_stat_grouped(
  y, yrep_prior[1:500, ], group = sites$sand_ratio, binwidth = 0.5
  ) +
  coord_cartesian(xlim = c(-4, 4))
ppc_stat_grouped(
  y, yrep_prior[1:500, ], group = sites$substrate_depth, binwidth = 0.5
  ) +
  coord_cartesian(xlim = c(-4, 4))
```

@@

```{r effect-sizes, message = FALSE}
posterior1 %>%
  posterior::summarize_draws() %>%
  knitr::kable()
emm <- emmeans(
  m_1, revpairwise ~ target_type + sand_ratio | exposition | survey_year_fct,
  type = "response"
  )
emm$emmeans
```

```{r write-csv, echo = FALSE}
draws1 %>% write_csv(here("outputs", "statistics", "table_fcs.csv"))
```
